---
title: "ShinyApplication Pitch"
author: "Nuria"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## INTRO

The objective of this App is visualization of the dependency of the miles/gallon figure for different car models with 3 different characteristics: number of cylinders, gear and whether if they are automatic or manual. 

## INPUT

You need to give this input to the app:
```{r echo = FALSE}
library(shiny)
library(datasets)

selectInput("variable", "Observed Characteristic:",
                    list("Cylinders" = "cyl", 
                         "Gears" = "gear",
                         "Transmission" = "am"))
```

## OUTPUT

As the output from the app, you will get plot of the miles per gallon value versus de parameter selected as the input.
```{r echo = FALSE}
mpgData <- mtcars
mpgData$am <- factor(mpgData$am, labels = c("Automatic", "Manual"))

# Define server logic required to plot various variables against mpg
shinyServer(function(input, output) {
        
        # Compute the forumla text in a reactive expression
        formulaText <- reactive({
                paste("mpg ~", input$variable)
        })
        
        # Return the formula text for printing as a title
        output$title <- renderText({
                formulaText()
        })
        
        # Generate a plot 
        output$mpgPlot <- renderPlot({
                
                plot(formula = as.formula(formulaText()), 
                     data = mpgData,
                     xlab = input$variable,
                     ylab = "mpg",
                     type="p",
                     col = "black")
        })
})
```

## THANK YOU



